Personality and political beliefs across the lifespan

### 2019-12-10 scripts/manuscript.tex
Merge conflicts

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\hypertarget{material}{%
\subsection{Material}\label{material}}

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

We used R (Version 3.6.1; R Core Team, 2019) and the R-packages \emph{\}MBESS} {[}@\}R-MBESS{]}, \emph{dplyr} (Version 0.8.3; Wickham et al., 2019), \emph{forcats} (Version 0.4.0; Wickham, 2019a), \emph{ggplot2} (Version 3.2.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{janitor} (Version 1.2.0; Firke, 2019), \emph{knitr} (Version 1.25; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{psych} (Version 1.8.12; Revelle, 2018), \emph{purrr} (Version 0.3.2; Henry \& Wickham, 2019), \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019b), \emph{tibble} (Version 2.1.3; Müller \& Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), \emph{tidyverse} (Version 1.2.1; Wickham, 2017), \emph{viridis} (Version 0.5.1; Garnier, 2018a, 2018b), and \emph{viridisLite} (Version 0.3.0; Garnier, 2018b) for all our analyses.

\hypertarget{results}{%
\section{Results}\label{results}}

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

\hypertarget{references}{%
\section{References}\label{references}}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-R-papaja}{}%
Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}

\leavevmode\hypertarget{ref-R-rio}{}%
Chan, C.-h., Chan, G. C., Leeper, T. J., \& Becker, J. (2018). \emph{Rio: A swiss-army knife for data file i/o}.

\leavevmode\hypertarget{ref-R-janitor}{}%
Firke, S. (2019). \emph{Janitor: Simple tools for examining and cleaning dirty data}. Retrieved from \url{https://CRAN.R-project.org/package=janitor}

\leavevmode\hypertarget{ref-R-viridis}{}%
Garnier, S. (2018a). \emph{Viridis: Default color maps from 'matplotlib'}. Retrieved from \url{https://CRAN.R-project.org/package=viridis}

\leavevmode\hypertarget{ref-R-viridisLite}{}%
Garnier, S. (2018b). \emph{ViridisLite: Default color maps from 'matplotlib' (lite version)}. Retrieved from \url{https://CRAN.R-project.org/package=viridisLite}

\leavevmode\hypertarget{ref-R-purrr}{}%
Henry, L., \& Wickham, H. (2019). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}

\leavevmode\hypertarget{ref-R-here}{}%
Müller, K. (2017). \emph{Here: A simpler way to find your files}. Retrieved from \url{https://CRAN.R-project.org/package=here}

\leavevmode\hypertarget{ref-R-tibble}{}%
Müller, K., \& Wickham, H. (2019). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}

\leavevmode\hypertarget{ref-R-psych}{}%
Revelle, W. (2018). \emph{Psych: Procedures for psychological, psychometric, and personality research}. Evanston, Illinois: Northwestern University. Retrieved from \url{https://CRAN.R-project.org/package=psych}

\leavevmode\hypertarget{ref-R-ggplot2}{}%
Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}

\leavevmode\hypertarget{ref-R-tidyverse}{}%
Wickham, H. (2017). \emph{Tidyverse: Easily install and load the 'tidyverse'}. Retrieved from \url{https://CRAN.R-project.org/package=tidyverse}

\leavevmode\hypertarget{ref-R-forcats}{}%
Wickham, H. (2019a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}

\leavevmode\hypertarget{ref-R-stringr}{}%
Wickham, H. (2019b). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}

\leavevmode\hypertarget{ref-R-dplyr}{}%
Wickham, H., François, R., Henry, L., \& Müller, K. (2019). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}

\leavevmode\hypertarget{ref-R-tidyr}{}%
Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}

\leavevmode\hypertarget{ref-R-readr}{}%
Wickham, H., Hester, J., \& Francois, R. (2018). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}

\leavevmode\hypertarget{ref-R-knitr}{}%
Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.). Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from \url{https://yihui.name/knitr/}

@@

\includegraphics{manuscript_files/figure-latex/correlations-1.pdf}

>>>>

\section{Methods}\label{methods}

\subsection{Participants}\label{participants}

\subsection{Material}\label{material}

\subsection{Procedure}\label{procedure}

\subsection{Data analysis}\label{data-analysis}

We used R (Version 3.6.1; R Core Team, 2019) and the R-packages
\emph{\}MBESS} {[}@\}R-MBESS{]}, \emph{dplyr} (Version 0.8.3; Wickham,
François, Henry, \& Müller, 2019), \emph{forcats} (Version 0.4.0;
Wickham, 2019a), \emph{ggplot2} (Version 3.2.1; Wickham, 2016),
\emph{here} (Version 0.1; Müller, 2017), \emph{janitor} (Version 1.2.0;
Firke, 2019), \emph{knitr} (Version 1.25; Xie, 2015), \emph{papaja}
(Version 0.1.0.9842; Aust \& Barth, 2018), \emph{psych} (Version 1.8.12;
Revelle, 2018), \emph{purrr} (Version 0.3.3; Henry \& Wickham, 2019),
\emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018),
\emph{rio} (Version 0.5.16; C.-h. Chan, Chan, Leeper, \& Becker, 2018),
\emph{stringr} (Version 1.4.0; Wickham, 2019b), \emph{tibble} (Version
2.1.3; Müller \& Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \&
Henry, 2019), \emph{tidyverse} (Version 1.2.1; Wickham, 2017),
\emph{viridis} (Version 0.5.1; Garnier, 2018a, 2018b), and
\emph{viridisLite} (Version 0.3.0; Garnier, 2018b) for all our analyses.

\section{Results}\label{results}

@@

\section{Discussion}\label{discussion}

@@

\section{References}\label{references}

@@

\hypertarget{refs}{}
\hypertarget{ref-R-papaja}{}
Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with
R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}

\hypertarget{ref-R-rio}{}
Chan, C.-h., Chan, G. C., Leeper, T. J., \& Becker, J. (2018).
\emph{Rio: A swiss-army knife for data file i/o}.

\hypertarget{ref-R-janitor}{}
Firke, S. (2019). \emph{Janitor: Simple tools for examining and cleaning
dirty data}. Retrieved from
\url{https://CRAN.R-project.org/package=janitor}

\hypertarget{ref-R-viridis}{}
Garnier, S. (2018a). \emph{Viridis: Default color maps from
'matplotlib'}. Retrieved from
\url{https://CRAN.R-project.org/package=viridis}

\hypertarget{ref-R-viridisLite}{}
Garnier, S. (2018b). \emph{ViridisLite: Default color maps from
'matplotlib' (lite version)}. Retrieved from
\url{https://CRAN.R-project.org/package=viridisLite}

\hypertarget{ref-R-purrr}{}
Henry, L., \& Wickham, H. (2019). \emph{Purrr: Functional programming
tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}

\hypertarget{ref-R-here}{}
Müller, K. (2017). \emph{Here: A simpler way to find your files}.
Retrieved from \url{https://CRAN.R-project.org/package=here}

\hypertarget{ref-R-tibble}{}
Müller, K., \& Wickham, H. (2019). \emph{Tibble: Simple data frames}.
Retrieved from \url{https://CRAN.R-project.org/package=tibble}

\hypertarget{ref-R-base}{}
R Core Team. (2019). \emph{R: A language and environment for statistical
computing}. Vienna, Austria: R Foundation for Statistical Computing.
Retrieved from \url{https://www.R-project.org/}

\hypertarget{ref-R-psych}{}
Revelle, W. (2018). \emph{Psych: Procedures for psychological,
psychometric, and personality research}. Evanston, Illinois:
Northwestern University. Retrieved from
\url{https://CRAN.R-project.org/package=psych}

\hypertarget{ref-R-ggplot2}{}
Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}.
Springer-Verlag New York. Retrieved from
\url{https://ggplot2.tidyverse.org}

\hypertarget{ref-R-tidyverse}{}
Wickham, H. (2017). \emph{Tidyverse: Easily install and load the
'tidyverse'}. Retrieved from
\url{https://CRAN.R-project.org/package=tidyverse}

\hypertarget{ref-R-forcats}{}
Wickham, H. (2019a). \emph{Forcats: Tools for working with categorical
variables (factors)}. Retrieved from
\url{https://CRAN.R-project.org/package=forcats}

\hypertarget{ref-R-stringr}{}
Wickham, H. (2019b). \emph{Stringr: Simple, consistent wrappers for
common string operations}. Retrieved from
\url{https://CRAN.R-project.org/package=stringr}

\hypertarget{ref-R-tidyr}{}
Wickham, H., \& Henry, L. (2019). \emph{Tidyr: Tidy messy data}.
Retrieved from \url{https://CRAN.R-project.org/package=tidyr}

\hypertarget{ref-R-dplyr}{}
Wickham, H., François, R., Henry, L., \& Müller, K. (2019). \emph{Dplyr:
A grammar of data manipulation}. Retrieved from
\url{https://CRAN.R-project.org/package=dplyr}

\hypertarget{ref-R-readr}{}
Wickham, H., Hester, J., \& Francois, R. (2018). \emph{Readr: Read
rectangular text data}. Retrieved from
\url{https://CRAN.R-project.org/package=readr}

\hypertarget{ref-R-knitr}{}
Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.).
Boca Raton, Florida: Chapman; Hall/CRC. Retrieved from
\url{https://yihui.name/knitr/}

@@

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/correlations-1.pdf}
\caption{}
\end{figure}
